Reproducibility of HCP pipelines across operating systems

### 2016-10-28 paper.tex
Added a comment on FSL installation
More comments in sections 2 and 3.

\author{Lalet Scaria, Lindsay B. Lewis, Tristan Glatard}

@@

\subsection{General framework}

We installed the pipelines in three versions of Linux using Docker containers.

@@

We executed the pipelines on Compute Canada.

@@

Report on versions used and any other specificity such as dependencies (e.g. explain why they depend on gcc).

@@

>>>>

\author{Lalet Scaria, Lindsay B. Lewis, Alan C. Evans, Tristan Glatard}

@@

\subsection{Dataset}

@@

@@

We installed the pipelines in three versions of Linux using Docker
containers. Refer to (immutable) version of containers used. Make sure
the exact same containers are used for all subjects (no rebuild as
rebuild would trigger package update). For each execution, we
monitored the list of packages used with versions.

\paragraph{Hardware.} We executed the pipelines on Compute Canada
using the Guillimin cluster of Calcul Qu\'ebec. We monitored the
hardware used (CPU and memory).

\paragraph{FSL installation.} We developed our own FSL installer to be
able to customize easily the FSL version and build (the script
provided by FSL installs the latest version by default). We used FSL
5.0.6, built for CentOS5 and CentOS6.

\paragraph{Execution.} The pipeline was launched twice in the same
environment to detect any use of pseudo-random numbers. We
made sure that the results produced by these two executions were
identical.

@@

Show lists of packages used with version. Focus on important
differences (e.g.: python interpreter, gcc if relevant) and explain
why these packages are important.
